Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-04 doc/sc2012/experiments.tex
fixed systems table

The efficiency and scalability of Legion was examined by measuring the performance
of three applications on three clusters.  Table \ref{table:systems} summarizes 
the three clusters that were used.

\begin{tabular}{lccccc}
 & Nodes & CPUs/Node & GPUs/Node & DRAM/Node & Infiniband \\
sapling & 4 & 2x Xeon 5680 (HT enabled) & 2x Tesla C2070 & 48 GB & 2x QDR \\
viz & 10 & 2x Xeon 5680 (HT disabled) & 5x Quadro Q5000 & 24 GB & QDR \\
keeneland & 32* & 2x Xeon 5660 (HT disabled) & 3x Tesla M2090 & 24 GB & QDR 
\end{tabular}

>>>>

The efficiency and scalability of Legion was examined by measuring the performance
of three applications on three clusters.  The table in Figure~\ref{fig:systems} summarizes 
the three clusters that were used.

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & QDR \\
\end{tabular}
}
\label{fig:systems}
\caption{Configurations of Systems Used for Experiments}
\end{figure}
